### 2024-08-17 paper.tex
small fix in section 8

\section{Finding the irreducible components of \(U_0\)}
Let \(X\) be nilpotent with Jordan basis \((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}\).
Let \(V = \{(A_{a,b}, U) : \forall i. \; A_{a,b} U_{i + 1} \subseteq U\}\).
Let
\[U_0 = \{(A_{0,b}, U) \in V\}.\]
We will find the irreducible components of \(U_0\).
We note that even finding the irreducible components of \(\{A_{0,0}, U \in V\}\) is a pretty hard problem.
Not ambitious enough to try to re-solve that problem, we will use its solution.
\par To find the irreducible components of \(U_0\), we will use a known result about the irreducible components of the usual Springer fiber at an element \(J(\mu) \in \gl_{m + n}\).
(I should define this somewhere else, but \(J(\mu)\) just has the blocks in order of nonincreasing size.)
\begin{theorem}
    (Needs citation!)
    The irreducible components of the Springer fiber at \(J(\mu)\) are in bijection with the standard Young tableaus of shape \(\mu\).
    Further, the irreducible components are equidimensional, of dimension \(\sum_{i \neq j} \min(\mu_i, \mu_j) = \sum_i (i - 1) \mu_i\).
\end{theorem}
Let \(W_\mu\) denote the Springer fiber at \(J(\mu)\), and let \((W_{\mu, d})_d\) be the irreducible components.
We remark that the Springer fiber at \(PJ(\mu)P^{-1}\) is \(PW_\mu\), and its irreducible components are \((PW_{\mu, d})_d\).
We will use this result; to find the regular Springer fiber at any \(X \in \gl_{m + n}\), we just need to find \(P\) such that \(P^{-1}XP\) is in Jordan normal form; equivalently, we just need to find a Jordan basis for \(X\).
\par So, our strategy will be to find a subset of \(U_0\) such that \(A_{0,b}\) has some fixed Jordan form \(\mu\), and we have an algebraic map \(b \mapsto P\) such that for \(A_{0,b}\) in the subset, \(PJ(\mu)P^{-1} = A_{0,b}\).
Then we can break this subset into irreducible components by putting the Springer fiber at \(b\) in correspondence with one of the \(W_{\mu,d}\).
I think this explanation of intuition is important, so I should try to make it better.
\par Finding the map \(b \mapsto P\) amounts to finding a Jordan basis for \(A_{0,b}\).
So, with this as our motivation, we find a Jordan basis for \(A_{0,b}\).

>>>>

\section{Finding the irreducible components of \(U_0\)}
Let \(X\) be nilpotent with Jordan basis \((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}\).
Let \(V = \{(A_{a,b}, U) : \forall i. \; A_{a,b} U_{i + 1} \subseteq U\}\).
Let
\[U_0 = \{(A_{0,b}, U) \in V\}.\]
We will find the irreducible components of \(U_0\).
We note that even finding the irreducible components of \(\{A_{0,0}, U \in V\}\) is a pretty hard problem.
Not ambitious enough to try to re-solve that problem, we will use its solution.
\par To find the irreducible components of \(U_0\), we will use a known result about the irreducible components of the usual Springer fiber at an element \(J(\mu) \in \gl_{m + n}\).
(I should define this somewhere else, but \(J(\mu)\) just has the blocks in order of nonincreasing size.)
\begin{theorem}
    (Needs citation!)
    The irreducible components of the Springer fiber at \(J(\mu)\) are in bijection with the standard Young tableaus of shape \(\mu\).
    Further, the irreducible components are equidimensional, of dimension \(\sum_{i \neq j} \min(\mu_i, \mu_j) = \sum_i (i - 1) \mu_i\).
\end{theorem}
Let \(W_\mu\) denote the Springer fiber at \(J(\mu)\), and let \((W_{\mu, d})_d\) be the irreducible components.
We remark that the Springer fiber at \(PJ(\mu)P^{-1}\) is \(PW_\mu\), and its irreducible components are \((PW_{\mu, d})_d\).
We will use this result; to find the regular Springer fiber at any \(X \in \gl_{m + n}\), we just need to find \(P\) such that \(P^{-1}XP\) is in Jordan normal form; equivalently, we just need to find a Jordan basis for \(X\).
\par So, our strategy will be to find a subset of the possible values of \(b\) such that \(A_{0,b}\) has some fixed Jordan form \(\mu\), and we have an algebraic map \(b \mapsto P_b\) such that for \(A_{0,b}\) in the subset, \(P_bJ(\mu)P_b^{-1} = A_{0,b}\).
Then we obtain an irreducible component by picking one of these subsets of the possible values of \(b\) and picking a Springer fiber at \(J(\mu)\).
\par Finding the map \(b \mapsto P\) amounts to finding a Jordan basis for \(A_{0,b}\).
So, with this as our motivation, we find a Jordan basis for \(A_{0,b}\).
